Cleaned Stop Data

### 2016-08-08 eda/CensusDataExploration/HeatmapExploration3.Rmd
organizing folders

```{r, include = FALSE, echo = FALSE}
library(sp)
library(ggmap)
library(tidyr)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(readr)
library(maps)
library(mapdata)
library(rgdal)
library(rgeos)
#library(gpclib)       # loads polygon clipping library
library(maptools)     # loads sp library too
library(RColorBrewer) # creates nice color schemes
library(classInt)     # finds class intervals for continuous variables
library(gdata)
library(XLConnect)
#library(data.table)
```

@@

### Get the regular Berkeley map:
```{r,include = F, echo = FALSE}
# get rid of the axes:
ditch_the_axes <- theme(
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  panel.border = element_blank(),
  panel.grid = element_blank(),
  axis.title = element_blank()
  )
```
```{r,include = F, echo = FALSE}
# get the plain Berkeley map from Google:
berkMap = map = get_map(location = c( lon = mean(lonvals), lat = mean(latvals) ), zoom = 12) 
```

```{r}
berkgg <-ggmap(berkMap) +
  xlim(-122.335, lonmax) + ylim(latvals) +
  ditch_the_axes 
berkgg
```

@@

```{r}
popdenmap <- ggmap(berkMap) + 
  geom_polygon(data = census.df_pop, aes(x = long, y = lat, group = group, fill = TotalPop), color = "white", alpha = .7) 
popdenmap
```

>>>>

```{r, include = FALSE, echo = FALSE}
library(sp)
library(ggmap)
library(tidyr)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(readr)
library(maps)
library(mapdata)
library(rgdal)
library(rgeos)
#library(gpclib)       # loads polygon clipping library
library(maptools)     # loads sp library too
library(RColorBrewer) # creates nice color schemes
library(classInt)     # finds class intervals for continuous variables
library(gdata)
library(XLConnect)
library(data.table)
```

@@

### Get the regular Berkeley map:
```{r,include = F, echo = FALSE}
# get rid of the axes:
ditch_the_axes <- theme(
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  panel.border = element_blank(),
  panel.grid = element_blank(),
  axis.title = element_blank()
  )

# get the plain Berkeley map from Google:
berkMap = map = get_map(location = c( lon = mean(lonvals), lat = mean(latvals) ), zoom = 12)

berkgg <-ggmap(berkMap) +
  xlim(-122.335, lonmax) + ylim(latvals) +
  ditch_the_axes 
berkgg
```

@@

```{r}
popdenmap <- berkgg + 
  geom_polygon(data = census.df_pop, aes(x = long, y = lat, group = group, fill = TotalPop), color = "white", alpha = .7) 
popdenmap
```

### 2016-08-08 eda/JailAndArrestExploration/Jail.Rmd
organizing folders

ggplot(najail)+
  geom_bar(aes(x=Disposition,
               fill = Race))+
  facet_wrap(~Sex)

>>>>

najail$Disposition <- str_replace(najail$Disposition, "NO COMPLAINT", "NC") %>% 
  str_replace("SANTA RITA JAIL", "SRC") %>% 
  str_replace("")

ggplot(najail)+
  geom_bar(aes(x=Disposition,
               fill = Race))+
  facet_wrap(~Sex)+
   scale_x_discrete(labels = function(x) str_wrap(x, width = 5))

### 2016-08-08 eda/StopDataExploration/Berkeley_PD_Stop.Rmd
organizing folders

>>>>

totalIncidentsNumber <- nrow(stop_df)
typeone <- stop_df %>%
    filter(Other == "" & Dispositions != "")
typeoneNumber = nrow(typeone)
typetwo <- stop_df %>%
    filter(Other != "" & Dispositions == "")
typetwoNumber = nrow(typetwo)
typethree <- stop_df %>%
    filter(Other != "" & Dispositions != "")
typethreeNumber = nrow(typethree)
